%%MaD.tex - Notes taken for Materials and Devices Lecture
%%Author: Andy Goetz
%%Date Modified: 10-7-09
%%License: Ask me before reproducing/modifying, etc.


\documentclass{article}

%Make sure you have the file ShumanNote.scy in the same directory as
%this one. It has contains the style sheet for ECE111, and is needed
%to standardize the layout of LateX documents created for the class.
\input{../Uncore.sty} 
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{tikz}
\usepackage{array}
\usepackage{program}
\usepackage{listings}
\pdfpagewidth 8.5in 
\pdfpageheight 11in
\usepackage{titlesec}
\usepackage{ucs}
\usepackage[utf8x]{inputenc}
%% \titleformat{\section}{\bfseries}{\thesection}{1em}{}
%% \titleformat{\subsection}{\bfseries}{\thesubsection}{1em}{}
%This package is used to line up pictures 
\usepackage{graphicx}
\usepackage{fancyvrb}
\usepackage{listings}
%allows cursive font
%\usepackage{amsmath}

%allows hyperlinks 
\usepackage{hyperref}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} 
%% \renewcommand\thesubsection{\alph{subsection})}
%% \renewcommand\thesection{\arabic{section})}

\begin{document}

\createtitle{Gameboy Graphics Proposal}
%% These commands allow me to use cursive letter for things such as
%% length.  Note that on ubuntu linux, this required installation of
%% the package 'texlive-fonts-extra'. 
%% Taken from
%% http://www.latex-community.org/forum/viewtopic.php?f=5&t=1404&start=0
\newenvironment{frcseries}{\fontfamily{frc}\selectfont}{}
\newcommand{\textfrc}[1]{{\frcseries#1}}
\newcommand{\mathfrc}[1]{\text{\textfrc{#1}}}




\section{Overview}
We plan on implementing the sprite-based graphics of the original
gameboy. The gameboy used raster graphics accessed through a simple,
memory mapped interface. We plan on creating an implmentation of these
graphics, and leveraging the new validation features of System Verilog
to accelerate the testing process. 

\section{Existing Work}
The internet is full of gameboy emulators. In addition, several
emulators have been created for FPGAs (i.e.
\url{https://github.com/trun/fpgaboy}). However, none of these designs
use System Verilog. We plan on using these designs as a jumping-off
point for our own implmentation.

\section{Requirements}

We plan on implementing the original gameboy's sprite-based raster
graphics engine. In addition to accepting draw commands from the
gameboy cpu, the graphics engine needs to provide interrupt signals to
the CPU. 

\section{Testing Methodology}



\end{document}

