
\section{Project Focus}
Our project will focus on the CPU core of a Gameboy using a previous project,
FPGABOY \footnote{FPGABOY - an implementation of a Gameboy system onto an FPGA 
writen in Verilog}. Another team will be focusing on peripherals for our project 
so that they can operate as a complete system. The CPU core, originally writen 
in Verilog, will be ported to use a synthesizable subset of System Verilog.
The synthesis target we will be focusing on will be on an Altera Cyclone II 
FPGA kit available in FAB 60-04\footnote{Part Number DK-CYCII-2C20N}.

\section{Testing}

Testing will use two modes from the Veloce Solo tools; the synthesizeable 
testbench and the TBX modes. The sythesizable testbench model will be used for 
automated module fuzz testing, while the TBX modes are going to be used for 
directed tests. For testbench data, there are test ROMs created 
for testing Gameboy emulators, which we can use to verify that our instruction 
set simulation is accurate. There are also timing tests within the test ROMs. 

For additional tests, we will be able to create test programs using the GBDK 
development kit and Gameboy assembler. The ultimate test will be the testing 
of released commercial roms after the two teams have intergrated the 
synthesizable code. set simulation is accurate. There are also timing tests 
within the test ROMs. For additional tests, we will be able to create test 
programs using the GBDK development kit and Gameboy assembler.
We also intend to use high-level testing constructs provided by SystemVerilog 
(e.g., assertions) to further verify the design, once these concepts are 
covered in class. 

\section{Integration and Other Group}
Both groups will be using different branches on the same git repository for 
quick integration. The sythesis project file will be shared between groups in 
an attempt to reduce the amount of redundant groups.
